\newgeometry{left=5cm, right=5cm, top=4cm}
	\thispagestyle{plain}
	\section*{\begin{center}
			\Huge{Foreword}
	\end{center}}
		To the astute reader, it should already be obvious that neither Yele'u University nor Mar-Ktu actually exist. For that matter, not one person or place mentioned in this book is to be found in the real world, unless something has changed very drastically since this book was penned. \textit{The Historical Encyclopedia of Mar-Ktu} is an orderly and itemized breakdown of the most critical concepts, people, and powers of a fictional world, written by nostalgic moderators and players of the now-defunct roleplaying subreddit /r/CivWorldPowers. In these pages, we the authors endeavor to expand and elaborate on the events of a nationbuilding play-by-post we still remember fondly, while simultaneously improving on the original to achieve a more cohesive world and more intricate detail. As we do this, we also try our hardest to remain completely in character.\par 
		
		Once you have finished this brief preamble, the entire book is written to resemble an actual publication in the field of World History from the esteemed Yele'u University in Pylona. This work has, of course, been translated from its original [LUX Creole] to English for your enjoyment and ease of reading. We hope you find the peoples, places, cultures, and conflicts of Mar-Ktu to be as interesting as we do. After all, they gripped us enough that we sat down to write a book. Two, in fact.\par 
		
		As a final note to readers, \textit{The Historical Encyclopedia of Mar-Ktu} exists as a companion piece to \textit{The History of Mar-Ktu}. While this book provides one with focused and consolidated information on individual topics of interest, the \textit{History} provides one with a chronological narrative that serves as a useful overview of this world's history. As this world is fabricated in its entirety, readers may find reading first through the \textit{History}, while searching for information on people and places here as the need should arise, to be a fast and effective way of acquiring a deeper comprehension of the subject matter than this book can provide alone. For this reason, we recommend perusing both books in conjunction.\par
		
		And now, without further ado, we hope you enjoy a look into the itemized history of a world both very much--and yet in many ways nothing--like our own. \par
		
		\clearpage  
\restoregeometry
\begin{multicols}{2}
	\tableofcontents
	\newpage
	\thispagestyle{plain}
	\chapter*{Introduction}
	\label{chap:intro}
	\addcontentsline{toc}{chapter}{\nameref{chap:intro}}
	
	\clearpage
\end{multicols}