	The Bulkhai Sahinate was the ruling body of the Bulkhan Peninsula - and later, the Tokkan Plains, Rokali highlands, and Il'Vagur Peninsula - between the years 196 and 717 AC. It is one of the longest lasting continuous governments in history and the longest one in southern Ma'at. The Sahinate was the last government which held a unified peninsula until the de-colonization period following the Millenium War and the establishment of the Bulkhai Republic. Although the capital Tinar was lost in 717, the Sahinate continued to survive under the rule of the Dragmar until 723, although this is not considered a part of the Bulkhai Sahinate but a successor.
	
	Following the Babuas' Coup against the Tinar Mubar Gezuar II, the Bulkhai Sahinate was established as a way for the religious elite of the peninsula to maintain an overbearing influence on the government, a status which they would maintain until Beliar's reforms in 363 AC. Between 196 and 363 AC, the Sahinate was ruled in a de-centralized fashion, with the Zoginates maintaining an increasing level of autonomy and the Zogs charged with ruling these regions were allowed increasing levels of power. The Babuas' influence on the Sahinate was greatly diminished following Enver's War (359 - 361 AC) and Beliar's reforms of 363, which granted the Sahin increased authority, expanded the number of ruling bodies was three to five, and worked to centralize authority within the capital while creating a meritocratic system of advancement. The reforms eventually allowed Bulkhai to spread far beyond the peninsula, gaining influence and territories in the Tokkan Plains, lower Rokali Highlands, and southwestern Kriovuh coastline.
	
	The expansion of the Bulkhai Sahinate came at a cost of stability, particularly in the high government. An increasing amount of internal squabbling saw the Zoginates and the Babuas openly in conflict for several decades, attempting to wrest power both from one another and from the Sahin himself. However, this expansion also allowed for Bulkhai to expand its horizons and establish more direct contact with states outside of the Bulkhan Ring. Voyages under Bulkhan explorers, in particular Barkabir Aimat, would lead to the exploration of southern Vinayaka, north Ma'at, and north Enki. 
	
	The late 400s saw a decline in Bulkhan "extravagances". Following the Battle of Altivo (472 AC), Bulkhai would not capture any new territory until after Ximal's ascension to the position of Sahin in 521 AC. Between 472 and 521, Bulkhai saw a substantial decrease in its standing army, a loss of several territories in the Mai-Mai coastline and the Rokali Highlands, the Sahinate navy to fall into disrepair, and an increasing dependence on slavery in Valona and Girok (despite the practice being illegal against other Dregunist worshippers). In particular, the rise of slavery coincided with several tax laws and an updated census which resulted in increased taxes for those with more workers under their command. As a result, raids from Valona and Girok into the Rokali lands were quite frequent, where both Dregunist and non-Dregunist worshippers would be taken and enslaved without being listed on the census.
	
	Following the Scribe's Revolt (520 AC) and Ximal's accession to position of Sahin (521 - 566 AC), Bulkhai saw a massive gain in territory within the Tokkan Ring. Ximal oversaw the addition of the entirety of the Il'Vagur Peninsula, Mai-Mai Plateau, and the Tokkan Angxaos. The Sahinate maintained very loose control over its new territories, preferring to allow much of its newly conquered regions a great amount of autonomy as long as taxes were paid and Bulkhai was recognized as the Chosen of the Dregunist Faith. Bulkhai's Golden Age continued with its expansion into the Rokali Highlands between 578-596 AC, ending following Il'Poal's Rebellion (617 - 632 AC).
	
	The 7th century saw the expansion of Pan Gu and Ullr trade throughout the world. Bulkhai, while not maintaining a completely isolationist stance, Bulkhai allowed foreign powers to lease ports within its borders, with Glimmer being allowed the vast majority of these ports. This increase in trade between 633 and 680 helped to maintain a declining empire. Bulkhai's lifespan was extended until the eruption of Maliri in 717 AC, which saw the complete loss of the High Government of Bulkhai and began the Wars of Bulkhan Succession, which signaled the beginning of the Feuding Cities Era and the end of the Bulkhai Sahinate.
	
\subsection{History}	
	\subsubsection{Founding}
		\paragraph{Decline of the Firiik Confederation}
			The exact starting point of the Firiik Mubarat Confederation's decline has eluded historians for centuries, with the question dating back to the early scholars of the Bulkhai Sahinate who yearned to answer the reason for their own government's power. There are a few main events which are favored: the abandonment of the Rumain Mubarat in 40 BC, ending a century-long attempt to colonize the Arberesh region with Firiik peoples; the Lashnar slave revolt of 28 BC, which began as a minor slave rebellion in the capital of the Mjerkin Mubarat that quickly ballooned and spread into the formation of the Lashnar Mubarat; the victory of the Lashnar Mubarat over the Confederation at the Battle of Uloshank that signaled the end of the First Lashnar-Firiik War (15-17 AC), which began an almost two-century long era of Lashnar dominance over the peninsula while the Confederation saw a continuous fall in prestige, territory, and authority. While these three events are popular, several others are also seriously considered. Whichever the case, the most common accepted theory is that the decline of the Confederation is impossible to pin down to any one event, emerging as a sum total of a continuous dependence of the Confederation on northern slaves, mercenary companies, increasing taxes on the poor majority, and over-extension of Firiik influence in regions which could not be continuously and properly defended. As a result, the final century before the First Conclave saw a slow but definite decline in the Firiik Mubarat Confederation, leaving behind a power vaccuum that would be filled first by the Lashnar Mubarat, and then the Tinar Mubarat.
			
			While the western Firiik Mubarats were embroiled in a 40-year long conflict with the Lashnar Mubarat, the eastern Mubarats afforded themselves more time and relative territorial safety. However, the economic burden of supporting the wester Mubarats in their conflicts against Lashnar forced the Allogron Mubar Erudazir (17 - 27 AC) to relinquish control of the northern territories which were under the rule of the Confederation, albeit with great autonomy. Under the Firiik Mubarats, the Arberesh region was ruled by local Fistins, led by the hierarchical Fis. With the abandonment of the Arberesh Fistins seemingly overnight, the Confederation allowed the Arberesh region to fall into a power vaccuum that would see both exogenous and indigenous powers vying for control and influence of the entirety.
		\paragraph{Rise of Tinar}
			As the Arberesh Fistins emerged from the departure of the southern Mubarats, a Fistin led by the Arberesh leader Tinarlar (? - 57 AC) emerged on the northern bank of the Mubarat River. Tinarlar's early life is masked in Bulkhan legend and myth, and not much is known about his origin or his early life apart from his possible Firiik ancestry. 
			
			Following the establishment of the Tinar Fistin, Tinarlar immediately went to war with the Maliri Fistin at the mouth of the Mubarat River, defeating it at the Battle of Maliri (22 AC). With this subjugation, Tinarlar proclaimed himself the chosen of the Dregunist faith by holding the holy Mountain, Malietr. Additionally he showed that the Confederation's presence in the Arberesh lands was truly no longer north of the Mubarat River. Following his victory against Maliri Tinarlar forged a friendship with the Kilibir Mubarat, a minor Mubarat south of the river which had grown disillusioned with the Confederation following continuous slights against it and defeats from without. With the aid of the Kilibirs, Tinarlar managed to win against the Deggestin Fistin further along the Mubarat River and established a strong hold on the northern bank by his death in 54 AC.
			
			In the century following Tinarlar's death, the Tinar Fistin would transform to a formal Muabrat and grow to encompass the entirety of the Arberesh region and extend south to conquer the former Allogron Mubarat and several of its dependent minors. Tinarlar's son, Clintir would expand north, capturing the city of Zid in 69 AC and expanding along the Bulkhan Sea coastline to the Suri River by the year 75 AC. Firiik scholars would migrate en masse to Tinar during Clintir's reign, following continuous internal strife within the Mubarats of the Confederation and providing Tinar with important cultural, historical, and administrative experts and educators. In 93 AC, Fis Tinef married the Kilibir noble Reinap and created the Tinar Mubarat, and managed to subjugate the Dunavidin Fistin by 100 AC. The Tinar Mubarat defeated the Firiik Mubarat Confederation at the Battle of Halif in 102 AC, following a string of other smaller victories against the Confederation. Gezuar's vicory over the League of Arber in 114 AC assured Tinar's dominance over the Arberesh region and established Tinar as the foremost power between the Mubarat and Suri Rivers.
			
			
		\paragraph{Tinar Expansion, Conflicts with Lashnar}
		\paragraph{Subjugation of Lashnar, Skudar}
		\paragraph{Unification with Valona}
	\subsubsection{Early Period}
		\paragraph{The Babuas and the Zoginates}
		\paragraph{Foreign Interventions}
	\subsubsection{Enver's Storm, War}
		\paragraph{Enver's Storm}
		\paragraph{Enver's War}
		\paragraph{Beliar's Reforms and Aftermath}
	\subsubsection{Beliar-Reform Period}
		\paragraph{Consolidation of authority}
		\paragraph{Expansion and Hegemony}
		\paragraph{Stagnation}
	\subsubsection{Ximal-Reform Period}
		\paragraph{Ximal, The Great: Early Life}
		\paragraph{Scribe's Revolt}
		\paragraph{Reform and Consolidation of Power}
		\paragraph{Expansion into the Il'Vagur Peninsula}
		\paragraph{Subjugation of the Mai-Mai Coastline and Plateau}
		\paragraph{The Tokkan Dragon Wars}
		\paragraph{Bulkahn Golen Age}
	\subsubsection{Decline}
		\paragraph{Global Exchange and Bulkhai}
				